Bootstrap learning via modular concept discovery

### 2013-04-22 drafts/ijcai2013/camera_ready/Dechter.IJCAI13.CameraReady.tex
Removed unused package declarations.
Added info about lexicographic ordering of Boolean functions in caption of the Boolean circuits distribution figure.

\usepackage{ijcai13}
\usepackage{times}
\usepackage{amsmath} 
\usepackage{amsfonts}
\usepackage{latexsym} 
\usepackage{ dsfont }
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{float}
\usepackage{circuitikz}
\usepackage{graphicx}
\usepackage[font=small]{subcaption}
\usepackage[font=small]{caption}
\usepackage{alltt}
\usepackage{dashrule}
\usepackage{array}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usetikzlibrary{arrows,automata, positioning, patterns,backgrounds}
\usetikzlibrary{arrows,shapes.gates.logic.US,shapes.gates.logic.IEC,calc}

@@

\maketitle
\begin{abstract}
%\small
 Suppose a learner is faced with a domain of problems about which it
 knows nearly nothing. It does not know the distribution of problems,
 the space of solutions is not smooth, and the reward signal is
 uninformative, providing perhaps a few bits of information but not
 enough to steer the learner effectively. How can such a learner ever
 get off the ground? A common intuition is that if the solutions to
 these problems share a common structure, and the learner can solve
 some simple problems by brute force, it should be able to extract
 useful components from these solutions and, by composing them,
 explore the solution space more efficiently. Here, we formalize this
 intuition, where the solution space is the space of typed functional
 programs and the gained information is stored as a stochastic grammar
 over programs. We propose an iterative procedure for exploring such
 spaces: in the first step of each iteration, the learner explores a
 finite subset of the domain, guided by a stochastic grammar; in the
 second step, the learner compresses the successful solutions from the
 first step to estimate a new stochastic grammar. We test this
 procedure on symbolic regression and Boolean circuit learning and
 show that the learner discovers modular concepts for these
 domains. Whereas the learner is able to solve almost none of the
 posed problems in the procedure's first iteration, it rapidly becomes
 able to solve a large number by gaining abstract knowledge of the
 structure of the solution space.

\end{abstract}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figures/circuitDistrComp2.png}
\caption{Distribution of Boolean functions among (a) the set of 1000
  circuits randomly constructed from AND, OR and NOT gates (see text);
  b) the first 1000 expressions from the grammar over expressions
  \emph{before} learning; c) the first 1000 expressions from the
  grammar over expressions \emph{after} learning. Gray levels indicate
  percent of instances (circuits/expressions) which evaluate to that
  function.\label{fig:booldistr}}
\end{figure}

@@

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
\bibliography{ijcai13}
%% \nocite{*}

>>>>

\usepackage{ijcai13}
\usepackage{amsmath} 
\usepackage{amsfonts}
\usepackage{tikz} % don't have to include
\usepackage{tikz-qtree}
\usepackage[font=small]{subcaption}
\usepackage[font=small]{caption}
\usepackage{dashrule} 
\usetikzlibrary{arrows,automata, positioning, patterns,backgrounds}
\usetikzlibrary{arrows,shapes.gates.logic.US,shapes.gates.logic.IEC,calc}

@@

\maketitle
\begin{abstract}
 Suppose a learner is faced with a domain of problems about which it
 knows nearly nothing. It does not know the distribution of problems,
 the space of solutions is not smooth, and the reward signal is
 uninformative, providing perhaps a few bits of information but not
 enough to steer the learner effectively. How can such a learner ever
 get off the ground? A common intuition is that if the solutions to
 these problems share a common structure, and the learner can solve
 some simple problems by brute force, it should be able to extract
 useful components from these solutions and, by composing them,
 explore the solution space more efficiently. Here, we formalize this
 intuition, where the solution space is the space of typed functional
 programs and the gained information is stored as a stochastic grammar
 over programs. We propose an iterative procedure for exploring such
 spaces: in the first step of each iteration, the learner explores a
 finite subset of the domain, guided by a stochastic grammar; in the
 second step, the learner compresses the successful solutions from the
 first step to estimate a new stochastic grammar. We test this
 procedure on symbolic regression and Boolean circuit learning and
 show that the learner discovers modular concepts for these
 domains. Whereas the learner is able to solve almost none of the
 posed problems in the procedure's first iteration, it rapidly becomes
 able to solve a large number by gaining abstract knowledge of the
 structure of the solution space.
\end{abstract}

@@

\begin{figure}
\vspace{.5cm}
\includegraphics[width=\linewidth]{figures/circuitDistrComp2.png}
\caption{Distribution of Boolean functions among (a) the set of 1000
  circuits randomly constructed from AND, OR and NOT gates (see text);
  b) the first 1000 expressions from the grammar over expressions
  \emph{before} learning; c) the first 1000 expressions from the
  grammar over expressions \emph{after} learning. Gray levels indicate
  percent of instances (circuits/expressions) which evaluate to that
  function. Functions increase in domain size from left to right; each
  function can be represented as a binary string corresponding to the
  output column of the truth table, and functions are ordered with
  respect to these strings. \label{fig:booldistr}}
\end{figure}

@@

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
\bibliography{Dechter.IJCAI13.CameraReady}
%% \nocite{*}
